\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2020-10-24 doc/USER_MANUAL/04_creating_databases.tex

TODO / future work to do: currently the \texttt{BROADCAST\_SAME\_MESH\_AND\_MODEL}
option assumes to have the (master) mesh files in \texttt{run0001/DATABASES\_MPI} or
\texttt{run0001/OUTPUT\_FILES/DATABASES\_MPI}.
However, for adjoint runs you still need a \texttt{DATABASES\_MPI/} folder in each of the sub-runs directories,
e.g. \texttt{run0002/DATABASES\_MPI}, etc. to store the forward wavefields, kernels etc. of each sub-run.
This would not be needed for forward simulations.

>>>>

TODO / future work to do: currently the \texttt{BROADCAST\_SAME\_MESH\_AND\_MODEL}
option assumes to have the (main) mesh files in \texttt{run0001/DATABASES\_MPI} or
\texttt{run0001/OUTPUT\_FILES/DATABASES\_MPI}.
However, for adjoint runs you still need a \texttt{DATABASES\_MPI/} folder in each of the sub-runs directories,
e.g. \texttt{run0002/DATABASES\_MPI}, etc. to store the forward wavefields, kernels etc. of each sub-run.
This would not be needed for forward simulations.

### 2020-10-24 doc/USER_MANUAL/09_noise_simulations.tex
adds version info; removes white space

\texttt{STATIONS} remains the same as in previous earthquake simulations,
except that the order of receivers listed in \texttt{STATIONS} is
now important. The order will be used to determine the `master' receiver,
i.e., the one that simultaneously cross correlates with the others.\\

@@

\item Create a file called \texttt{./NOISE\_TOMOGRAPHY/irec\_master\_noise}.
Note that this file is located in directory \texttt{./NOISE\_TOMOGRAPHY/}
as well. In general, all noise simulation related parameter files
go into that directory. \texttt{irec\_master\_noise} contains only
one integer, which is the ID of the `master' receiver. For example,
if this file contains 5, it means that the fifth receiver listed in
\texttt{DATA/STATIONS} becomes the `master'. That's why we mentioned
previously that the order of receivers in \texttt{DATA/STATIONS} is
important.

Note that in some simulations, the \texttt{DATA/STATIONS} might
contain receivers which are outside of our computational domains.
Therefore, the integer in \texttt{irec\_master\_noise} is actually
the ID in \texttt{DATA/STATIONS\_FILTERED} (which is generated by
\texttt{bin/xgenerate\_databases}).

\item Create a file called \texttt{./NOISE\_TOMOGRAPHY/nu\_master}.
This file holds three numbers, forming a (unit) vector. It describes
which component we are cross-correlating at the `master' receiver,
i.e., ${\hat{{\bf \nu}}}^{\alpha}$ in \citet{trompetal2010}. The
three numbers correspond to E/N/Z components respectively. Most often,
the vertical component is used, and in those cases the three numbers
should be 0, 0 and 1.

@@

The simulated ensemble cross correlations are obtained after the second
simulation (Step 2). Seismograms in \texttt{OUTPUT\_FILES/} are actually
the simulated ensemble cross correlations. Collect them immediately
after Step 2, or the Step 3 will overwrite them. Note that we have
a `master' receiver specified by \texttt{irec\_master\_noise}, the
seismogram at one station corresponds to the cross correlation between
that station and the `master'. Since the seismograms have three components,
we may obtain cross correlations for different components as well,
not necessarily the cross correlations between vertical components.\\

>>>>

\texttt{STATIONS} remains the same as in previous earthquake simulations,
except that the order of receivers listed in \texttt{STATIONS} is
now important. The order will be used to determine the `main' receiver,
i.e., the one that simultaneously cross correlates with the others.\\

@@

\item Create a file called \texttt{./NOISE\_TOMOGRAPHY/irec\_main\_noise}.
Note that this file is located in directory \texttt{./NOISE\_TOMOGRAPHY/}
as well. In general, all noise simulation related parameter files
go into that directory. \texttt{irec\_main\_noise} contains only
one integer, which is the ID of the `main' receiver. For example,
if this file contains 5, it means that the fifth receiver listed in
\texttt{DATA/STATIONS} becomes the `main'. That's why we mentioned
previously that the order of receivers in \texttt{DATA/STATIONS} is
important.

Note that in some simulations, the \texttt{DATA/STATIONS} might
contain receivers which are outside of our computational domains.
Therefore, the integer in \texttt{irec\_main\_noise} is actually
the ID in \texttt{DATA/STATIONS\_FILTERED} (which is generated by
\texttt{bin/xgenerate\_databases}).

\item Create a file called \texttt{./NOISE\_TOMOGRAPHY/nu\_main}.
This file holds three numbers, forming a (unit) vector. It describes
which component we are cross-correlating at the `main' receiver,
i.e., ${\hat{{\bf \nu}}}^{\alpha}$ in \citet{trompetal2010}. The
three numbers correspond to E/N/Z components respectively. Most often,
the vertical component is used, and in those cases the three numbers
should be 0, 0 and 1.

@@

The simulated ensemble cross correlations are obtained after the second
simulation (Step 2). Seismograms in \texttt{OUTPUT\_FILES/} are actually
the simulated ensemble cross correlations. Collect them immediately
after Step 2, or the Step 3 will overwrite them. Note that we have
a `main' receiver specified by \texttt{irec\_main\_noise}, the
seismogram at one station corresponds to the cross correlation between
that station and the `main'. Since the seismograms have three components,
we may obtain cross correlations for different components as well,
not necessarily the cross correlations between vertical components.\\
